### 2017-09-29 TF-vldb2018/sec-tsim.tex

\stitle{Dynamic top-$k$ team formation}. Given $P$, $G$, two positive integers $r$, $k$, the list $L_{k}(P,G)$ of top-$k$ perfect subgraphs for $P$ in $G$,
a set of pattern updates $\Delta P$ and a set of data updates $\Delta G$,
the {\em dynamic top-k team formation} problem, denoted by \dynteamF{(P, G, k, L_{k}, \Delta P, \Delta G)},
is to find a list of $k$ perfect subgraphs with the top-$k$ largest density for $P\oplus\Delta P$ in $G\oplus\Delta G$, via team simulation.

It is worth mentioned that the \dynteamF{} problem covers a broad range of dynamic conditions,
\ie handling continuous separate and simultaneous pattern and data updates.
Here $\oplus$ denotes applying changes $\Delta P$ to $P$ and $\Delta G$ to $G$.
 $P\oplus\Delta P$ and $G\oplus\Delta G$ denote the updated pattern and data graphs.

>>>>

\stitle{Dynamic top-$k$ team formation}. Given pattern $P$, data graph $G$, two positive integers $r$, $k$, the list $L_{k}(P,G)$ of top-$k$ perfect subgraphs for $P$ in $G$,
a set of pattern updates $\Delta P$ and a set of data updates $\Delta G$,
the {\em dynamic top-k team formation} problem, denoted by \dynteamF{(P, G, k, L_{k}, \Delta P, \Delta G)},
is to find a list of $k$ perfect subgraphs with the top-$k$ largest density for $P\oplus\Delta P$ in $G\oplus\Delta G$, via team simulation.

It is worth mentioning that \dynteamF{} covers a broad range of dynamic situations,
\ie handling continuous separate and simultaneous pattern and data updates.
Here $\oplus$ denotes applying changes $\Delta P$ to $P$ and $\Delta G$ to $G$, and
 $P\oplus\Delta P$ and $G\oplus\Delta G$ denote the updated pattern and data graphs.
